---
output:
  html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```
<style type="text/css">
div.main-container {
  max-width: 2000px;
  margin-left: 0;
  margin-right: auto;
}
</style>
<style>
.tocify {
color: black;
}
<!-- } -->
<!-- .tocify .tocify-header { -->
<!--     position: fixed; -->
<!--     <!-- top: 50px; --> -->
<!--     left: 50px; -->
<!--     width: 350px; -->
<!--     <!-- border: solid 3px black; --> -->
<!--     <!-- height: 200px; --> -->
<!--  border: none; -->
<!-- } -->
.tocify .tocify-header .active {
color: white;
background: #d80b8c;
font-weight: bold;
}
<!-- .tocify .tocify-item { -->
<!-- background: white; -->
<!-- color: black; -->
<!--  border: none; -->
<!-- } -->
</style>
<style>
  .nav-pills>li>a:hover, .nav-pills>li>a:focus, .nav-pills>li.active>a,     .nav-pills>li.active>a:hover, .nav-pills>li.active>a:focus{
     background-color: #212070;
     }
</style>
<style>
.container { width: 1800px; }
h2 {
  background-color: #dddedd;
  color: black;
  text-indent: 20px;
  <!-- font-weight: bold; -->
}
h3 {
  background-color: #f2f2f2;
  color: black;
  text-indent: 20px;
  <!-- font-weight: bold; -->
}
h4 {
  <!-- background-color: #dddedd; -->
  <!-- color: black; -->
  text-indent: 50px;
  <!-- font-weight: bold; -->
}
</style>
<style>
.blackbox {
  padding: 1em;
  background: white;
  color: black;
  border: 2px solid #7f7f7f;
  width: 100%;
  position: center;
  align: center;
  margin: 0px auto;
}
.center {
  text-align: left;
  margin: 0px auto;
}
</style>
<!-- ```{css toc-content, echo = FALSE} -->
<!-- #TOC { -->
<!--   right: 270px; -->
<!--   margin: 20px 0px 25px 0px; -->
<!-- } -->
<!-- .main-container { -->
<!--     margin-left: 200px; -->
<!-- } -->
<!-- ``` -->
```{r Load Packages, echo = FALSE, warning = FALSE, message = FALSE}

# # Load packages -----------------------------------------------------------------------------------
suppressMessages({
  memory.limit(size = 8000000)
  library(readxl)
  library(writexl)
  library(plyr)
  library(dplyr)
  library(data.table)
  library(zoo)
  library(shiny)
  library(shinydashboard)
  library(shinydashboardPlus)
  library(shinyWidgets)
  library(htmlwidgets)
  library(lubridate)
  library(tcltk)
  library(tidyverse)
  library(plotly)
  library(knitr)
  library(kableExtra)
  library(leaflet)
  library(grid)
  library(gridExtra)
  library(eeptools)
  library(ggQC)
  library(zipcodeR)
  library(utils)
  library(scales)
  library(chron)
  library(bupaR)
  library(shiny)
  library(DT)
  library(DiagrammeR)
  library(shinyalert)
  library(edeaR)
  library(processmapR)
  library(processmonitR)
  library(processanimateR)
  library(tidyr)
  library(lubridate)
  library(RColorBrewer)
  library(DiagrammeR)
  library(ggplot2)
  library(leaflet)
  library(readr)
  library(highcharter)
  library(ggforce) # for 'geom_arc_bar'
  library(packcircles) # for packed circle graph
  library(viridis)
  library(ggiraph)
  library(treemapify)
  library(treemap)
  library(broom)
  library(extrafont)
  library(tis) # for US holidays
  library(vroom)
  library(sjmisc)
  library(tools)
  library(here)
  library(shinyBS)
  library(shinyscreenshot)
  library(fasttime)
  library(shinycssloaders)
  library(feather)
  # library(zipcodeR)
  library(formattable)
  library(shinyjs)
  library(janitor)
  library(patchwork)
  library(flexdashboard)
  # library(tidyverse)
  # library(viridis)
  # library(hrbrthemes)
  # library(plotly)
  # install.packages("bsts")
  library(bsts)
  library(reactable)
  # install.packages("reactablefmtr")
  library(reactablefmtr)
  library(svDialogs)
  # library(openxlsx)
  library(flextable)
  library(officedown)
  library(officer)
  library(magrittr)
  library(webshot) 
  library(png)
  library(ggh4x)
  library(RODBC)
  library(DBI)
  library(odbc)
  library(dbplyr)
  library(pool)
  library(emojifont)
  library(lubridate)
})

# devtools::install_github("hafen/lazyrmd")
# require(lazyrmd)
# 
# options(repos = c(tessera = "http://packages.tessera.io",
#   getOption("repos")))
# install.packages("lazyrmd")
# require(lazyrmd)

```


```{r Graph asthetics, echo = FALSE, warning = FALSE, message = FALSE}
### Color Functions for Graphs ============================================================

# Mount Sinai corporate colors "USE THIS TO ADD COLORS"
MountSinai_colors <- c(
  `dark purple`  = "#212070",
  `dark pink`    = "#d80b8c",
  `dark blue`    = "#00aeef",
  `dark grey`    = "#7f7f7f",
  `yellow`       = "#ffc000",
  `purple`       = "#7030a0",
  `med purple`   = "#5753d0",
  `med pink`     = "#f75dbe",
  `med blue`     = "#5cd3ff",
  `med grey`     = "#a5a7a5",
  `light purple` = "#c7c6ef",
  `light pink`   = "#fcc9e9",
  `light blue`   = "#c9f0ff",
  `light grey`   = "#dddedd"
  )

# Function to extract Mount Sinai colors as hex codes
# Use Character names of MountSinai_colors

MountSinai_cols <- function(...) {
  cols <- c(...)
  
  if (is.null(cols))
    return (MountSinai_colors)
  
  MountSinai_colors[cols]
}

# Color Function that can be used to call all colors is "MountSinai_cols()"
# Use in ggplot 

  #MountSinai_cols()       # will provide all colors and their hex codes in a table 
  #MountSinai_cols("pink") # will provide color name and the hex code for the pink color

# Create palettes 
MountSinai_palettes <- list(
  `all`   = MountSinai_cols("dark purple","dark pink","dark blue","dark grey",
                            "med purple","med pink","med blue","med grey", 
                            "light purple","light pink","light blue","light grey"),
  
  `main`  = MountSinai_cols("dark purple","dark pink","dark blue","dark grey"),
  
  `purple`  = MountSinai_cols("dark purple","med purple","light purple"),
  
  `pink`  = MountSinai_cols("dark pink","med pink","light pink"),
  
  `blue`  = MountSinai_cols("dark blue", "med blue", "light blue"),
  
  `grey`  = MountSinai_cols("dark grey", "med grey", "light grey"),
  
  `purpleGrey` = MountSinai_cols("dark purple", "dark grey"),
  
  `pinkBlue` = MountSinai_cols("dark pink", "dark blue")
  
)

# MountSinai_palettes
# Return function to interpolate a Mount Sinai color palette
# default value is the main palette, reverse = True will change the order

MountSinai_pal <- function(palette = "all", reverse = FALSE, ...) {
  pal <- MountSinai_palettes[[palette]]
  
  if (reverse) pal <- rev(pal)
  
  colorRampPalette(pal, ...)
}



# Scale Function for ggplot can be used instead of scale_color_manual
scale_color_MountSinai <- function(palette = "all", discrete = TRUE, reverse = FALSE, ...) {
  pal <- MountSinai_pal(palette = palette, reverse = reverse)
  
  if (discrete) {
    discrete_scale("colour", paste0("MountSinai_", palette), palette = pal, ...)
  } else {
    scale_color_gradientn(colours = pal(256), ...)
  }
}

# Scale Fill for ggplot insetead of scale_fill_manual 
scale_fill_MountSinai <- function(palette = "all", discrete = TRUE, reverse = FALSE, ...) {
  pal <- MountSinai_pal(palette = palette, reverse = reverse)

  if (discrete) {
    discrete_scale("fill", paste0("MountSinai_", palette), palette = pal, ...)
  } else {
    scale_fill_gradientn(colours = pal(256), ...)
  }
}

# Use in ggplot 
  # scale_color_MountSinai("main")

```


```{r Global Functions, echo = FALSE, warning = FALSE, message = FALSE}

'%!in%' <- function(x,y)!('%in%'(x,y)) # Does not include
not_all_na <- function(x) all(!is.na(x)) # Exclude columns with All NAs

```


```{r Data Connections, echo = FALSE, warning = FALSE, message = FALSE}

# Connection to Oracle DB ------------------------------------------------------
conn1 <- dbPool(drv = odbc(), dsn = "OAO Cloud DB SoYoun", timeout = 30)
conn3 <- dbPool(drv = odbc(), dsn = "OAO Cloud DB Production", timeout = 30)
conn2 <- dbConnect(odbc(), 
                  "Clarity_prod", 
                  uid = "kweons01" , 
                  pwd = "kweons01123$")
conn4 <- dbPool(drv = odbc(), dsn = "OAO Cloud DB Staging", timeout = 30)

conn5 <- dbConnect(odbc(),
                    Driver = "SQLServer",
                    # Server = "10.2.42.69", # old server
                    Server = "datahub-synapse.sql.azuresynapse.net",
                    database = "datahub_epic_dw",
                    UID = "MSS_USER",
                    PWD = "Apple_Bees456$",
                    Port = 1433)



# Clarity Connection  ------------------------------------------------
slot_raw_tbl <- tbl(conn2, "Y_DM_BOOKED_FILLED_RATE")
access_raw_tbl <- tbl(conn2, "MV_DM_PATIENT_ACCESS")
f_sched_appt_tbl <- tbl(conn2, "F_SCHED_APPT")
availability_raw_tbl <- tbl(conn2, "V_AVAILABILITY")
block_raw_tbl <- tbl(conn2, "AVAIL_BLOCK")
block_name_tbl <- tbl(conn2, "ZC_APPT_BLOCK")
orders_raw_tbl <- tbl(conn2, "ORDER_PROC")
visit_type_tbl <- tbl(conn2, "CL_PRC_VT_GROUPS")
visit_type_mapping_tbl <- tbl(conn2, "ZC_VISIT_TYPE_GRP")

dep_mapping_tbl <- tbl(conn2, "CLARITY_DEP")
dep_mapping <- dep_mapping_tbl %>%
  # dplyr::select(DEPARTMENT_ID, SPECIALTY) %>%
  collect()

clarity_ser_tbl <- tbl(conn2, "CLARITY_SER")
clarity_ser_2_tbl <- tbl(conn2, "CLARITY_SER_2")

finclass_tbl <- tbl(conn2, "V_PB_EPP_CUSTOM_PRD_TYPE")


# Local Connection ---------------------------------------------------
radiology_dep_mapping_tbl <- tbl(conn1, "RADIOLOGY_DEP_MAPPING")

clarity_ser_tbl_loc <- tbl(conn1, "CLARITY_SER")
clarity_ser_2_tbl_loc <- tbl(conn1, "CLARITY_SER_2")

dep_mapping_tbl_loc <- tbl(conn1, "CLARITY_DEP")

slot_data_raw_tbl <- tbl(conn1, "ALL_SLOTS")
slot_data_tbl <- tbl(conn1, "SLOT_DATA")
slot_data_prc_raw_tbl <- tbl(conn1, "ALL_SLOTS_PRC")
slot_data_prc_tbl <- tbl(conn1, "SLOT_DATA_PRC")

block_raw_tbl_loc <- tbl(conn1, "AVAIL_BLOCK")
block_name_tbl_loc <- tbl(conn1, "ZC_APPT_BLOCK")




#slot_view_tbl <- tbl(conn3, in_schema("OAO_PRODUCTION", "AMBULATORY_SLOT_TABLE"))


# Azure Connection ---------------------------------------------------
# access_raw_tbl <- tbl(conn5, in_schema("CLARITY", "MV_DM_PATIENT_ACCESS"))
# f_sched_appt_tbl <- tbl(conn5, dbplyr::ident_q('"CLARITY"."F_SCHED_APPT"'))
clarity_dep_conn <- tbl(conn5, dbplyr::ident_q('"Clarity"."CLARITY_DEP"'))

referrals_conn <- tbl(conn5, dbplyr::ident_q('"MS_SOLUTIONS_DEV"."y_s2_referrals_tmp"'))
caboodle_referrals_conn <- tbl(conn5, dbplyr::ident_q('"CABOODLE"."ReferralsDataView"'))
caboodle_referralFact_conn <- tbl(conn5, dbplyr::ident_q('"CABOODLE"."ReferralFact"'))
patient_conn <- tbl(conn5, dbplyr::ident_q('"CABOODLE"."PatientDim"'))
department_conn <- tbl(conn5, dbplyr::ident_q('"CABOODLE"."DepartmentDim"'))

clarity_referrals_tbl <- tbl(conn5, dbplyr::ident_q('"Clarity"."REFERRAL"'))
clarity_referrals_wq_tbl <- tbl(conn5, dbplyr::ident_q('"Clarity"."REFERRAL_WQ"'))

visitFact_conn <- tbl(conn5, dbplyr::ident_q('"Caboodle"."VisitFact"'))


```


```{r Analysis, echo = FALSE, warning = FALSE, message = FALSE}

CLARITY_SER_MYC


clarity_ser_dept <- tbl(conn5, dbplyr::ident_q('"Clarity"."CLARITY_SER_DEPT"')) %>%
  dplyr::select(PROV_ID, DEPARTMENT_ID, INACT_CAD_DEPT_YN) %>%
  left_join(tbl(conn5, dbplyr::ident_q('"Clarity"."CLARITY_SER"')) %>%
                  dplyr::select(PROV_ID, PROV_NAME, ACTIVE_STATUS, REFERRAL_SOURCE_TYPE)) %>%
  left_join(tbl(conn5, dbplyr::ident_q('"Clarity"."CLARITY_SER_2"')) %>%
              dplyr::select(PROV_ID, GENERIC_YN)) %>%
  left_join(tbl(conn5, dbplyr::ident_q('"Clarity"."CLARITY_DEP"')) %>%
                  dplyr::select(DEPARTMENT_ID, DEPARTMENT_NAME, SPECIALTY)) %>%
  left_join(tbl(conn5, dbplyr::ident_q('"Clarity"."MV_DM_PATIENT_ACCESS"')) %>%
              filter(year(CONTACT_DATE) == "2025") %>%
              filter(DERIVED_STATUS_DESC == "Arrived") %>%
              group_by(PROV_ID, DEPARTMENT_ID) %>%
              summarise(total_arrived_2025YTD = n()),
            by = c("PROV_ID", "DEPARTMENT_ID")) %>%
  # left_join(tbl(conn5, dbplyr::ident_q('"Clarity"."MV_DM_PATIENT_ACCESS"')) %>%
  #             filter(year(CONTACT_DATE) == "2025") %>%
  #             filter(DERIVED_STATUS_DESC == "Arrived") %>%
  #             group_by(DEPARTMENT_ID) %>%
  #             summarise(total_dept_arrived_2025YTD = n()),
  #           by = c("DEPARTMENT_ID")) %>%
  # filter(PROV_ID == "107754") %>%
  collect() %>%
  arrange(PROV_ID) %>%
  distinct()



clarity_ser_dept <- tbl(conn2, "CLARITY_SER_DEPT") %>%
  dplyr::select(PROV_ID, DEPARTMENT_ID, INACT_CAD_DEPT_YN) %>%
  left_join(tbl(conn2, "CLARITY_SER") %>%
                  dplyr::select(PROV_ID, PROV_NAME, ACTIVE_STATUS, REFERRAL_SOURCE_TYPE)) %>%
  left_join(tbl(conn2, "CLARITY_SER_2") %>%
              dplyr::select(PROV_ID, GENERIC_YN)) %>%
  left_join(tbl(conn2, "CLARITY_SER_MYC") %>%
              dplyr::select(PROV_ID, ALLW_OPEN_SCH_YN)) %>%
  left_join(tbl(conn2, "CLARITY_DEP") %>%
                  dplyr::select(DEPARTMENT_ID, DEPARTMENT_NAME, SPECIALTY)) %>%
  left_join(tbl(conn2, "MV_DM_PATIENT_ACCESS") %>%
              filter(year(CONTACT_DATE) == "2025") %>%
              filter(DERIVED_STATUS_DESC == "Arrived") %>%
              group_by(PROV_ID, DEPARTMENT_ID) %>%
              summarise(total_arrived_2025YTD = n()),
            by = c("PROV_ID", "DEPARTMENT_ID")) %>%
  # left_join(tbl(conn5, dbplyr::ident_q('"Clarity"."MV_DM_PATIENT_ACCESS"')) %>%
  #             filter(year(CONTACT_DATE) == "2025") %>%
  #             filter(DERIVED_STATUS_DESC == "Arrived") %>%
  #             group_by(DEPARTMENT_ID) %>%
  #             summarise(total_dept_arrived_2025YTD = n()),
  #           by = c("DEPARTMENT_ID")) %>%
  # filter(PROV_ID == "107754") %>%
  collect() %>%
  arrange(PROV_ID) %>%
  distinct()



slot_merged <- slot_data_prc_tbl %>%
  filter(year(SLOT_BEGIN_TIME) == "2025") %>%
  group_by(DEPARTMENT_ID, PROV_ID) %>%
  summarise(template_avail_min_2025YTD = sum(REG_AVAIL_MIN, na.rm = T)) %>%
  collect()

slot_merged_dept <- slot_data_prc_tbl %>%
  filter(year(SLOT_BEGIN_TIME) == "2025") %>%
  group_by(DEPARTMENT_ID) %>%
  summarise(dept_template_avail_min_2025YTD = sum(REG_AVAIL_MIN, na.rm = T)) %>%
  collect()


clarity_ser_dept_merged <- clarity_ser_dept %>%
  filter(!is.na(DEPARTMENT_NAME)) %>%
  filter(!str_detect(PROV_NAME, "ZZTEST")) %>%
  mutate(DEPARTMENT_ID = as.character(DEPARTMENT_ID)) %>%
  left_join(slot_merged %>%
              mutate(DEPARTMENT_ID = as.character(DEPARTMENT_ID))) %>%
  # left_join(slot_merged_dept %>%
  #             mutate(DEPARTMENT_ID = as.character(DEPARTMENT_ID))) %>%
  relocate(PROV_NAME, .after = "PROV_ID") %>%
  relocate(GENERIC_YN, .after = "PROV_NAME") %>%
  relocate(ACTIVE_STATUS, .after = "GENERIC_YN") %>%
  mutate(specialty_group = case_when(str_detect(SPECIALTY, "Cardiology") ~ "Cardiology", 
                                     str_detect(SPECIALTY, "OB/Gyn") | str_detect(SPECIALTY, "Obstetrics") | str_detect(SPECIALTY, "Gynecology") ~ "OB/Gyn",
                                     str_detect(SPECIALTY, "Dermatology") ~ "Dermatology",
                                     str_detect(SPECIALTY, "General Internal Medicine") | str_detect(SPECIALTY, "Family Medicine") ~ "Primary Care"
                                     ,TRUE ~ NA)) %>%
  group_by(PROV_ID) %>%
  mutate(specialty_combination = n_distinct(specialty_group[!is.na(specialty_group)])) %>%
  mutate(deactivated_dep = case_when(startsWith(DEPARTMENT_NAME, "X_") ~ "Y", TRUE ~ "N"),
         schedulable_dep = case_when(INACT_CAD_DEPT_YN == "Y" ~ "N", TRUE ~ "Y")) %>%
  mutate(remove_from_ser = case_when(deactivated_dep == "Y" | schedulable_dep == "N" ~ "Y", TRUE ~ "N")) 
  # mutate(dep_deactivation_required = case_when(deactivated_dep == "N" & (is.na(total_dept_arrived_2025YTD) | total_dept_arrived_2025YTD == 0) ~ "Y", TRUE ~ "N"))






check <- access_raw_tbl %>%
  head(10) %>%
  collect()
access <-  access_raw_tbl %>%
  group_by(DEPT_SPECIALTY_NAME, PROV_NAME_WID, VISIT_METHOD, VISIT_GROUP_NUM, PRC_NAME) %>%
  summarise(total = n()) %>%
  collect()

access2 <-  access_raw_tbl %>%
  group_by(DEPT_SPECIALTY_NAME, VISIT_METHOD, VISIT_GROUP_NUM, PRC_NAME) %>%
  summarise(total = n()) %>%
  collect()
  

template <- availability_raw_tbl %>%
  filter(PAT_ENC_CSN_ID == "100208888173") %>%
  collect()

```

